Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)

### 2025-08-05 resubmission/01-introduction.qmd
Revert "update resubmit"
This reverts commit 27ec0a816645e6bef02aa45f0b148543bc942541.

The justification of economic inequality has a long tradition in sociology, with seminal works such as the ones from Kluegel [-@kluegel_social_1995a; -@kluegel_beliefs_1986] and Lane [-@lane_political_1962; -@lane_market_1986]. Lane's main aim was to "help explain the tenacious hold of market capitalism on the public mind" [-@lane_market_1986, p.384], proposing the distinction between market and political justice. Whereas political justice refer to government actions aligned with justice principles such equality or need, market justice involves the allocation linked to earned desserts, particularly through individual contributions based on as effort and ability. Sociological survey research in this area has considered questions related to the extent to which it is considered just to get better access to social services (such as pensions, health and education) based on payment capacity [@busemeyer_skills_2014; @immergut_it_2020; @castillo_socialization_2024; @koos_moral_2019; @lindh_bringing_2023; @lindh_public_2015]. Although these services can be considered fundamental rights of citizenship, existing evidence indicates that a substantial share of the population legitimizes inequality in these domains, and that such preferences are shaped by individuals' socioeconomic characteristics as well as the broader contextual features of their countries [@koos_moral_2019; @lindh_public_2015; @busemeyer_skills_2014]. In the present paper, we argue that there are two other relevant factors to take into account when analyzing differences between individuals and groups to this regard: the perception of economic inequality and the perception of meritocracy.

@@

Along with perception of inequality, a second focus of this study is the perception of meritocracy. Meritocracy posits that inequality can be legitimized through distributive criteria such as effort and talent [@young_rise_1962; @davis_principles_2001]. Previous studies have demonstrated that people with stronger meritocratic beliefs tend to perceive less inequality as they attribute economic differences to individual achievements [@mijs_paradox_2021; @wilson_role_2003] and also to justify more inequality as these beliefs are associated with attitudes that legitimize status differences [@batruch_belief_2023]. In a context as Chile, where the distribution of goods and services is predominantly governed by market logics strongly introduced during the military dictatorship (1973-1989) [@madariaga_three_2020; @boccardo_30_2020], meritocratic perceptions have the potential to affect the acceptance of social inequalities. Therefore, incorporating the perception of meritocracy in this literature allows for an understanding of how attitudes toward inequality are shaped not only by the perception of economic gaps, but also by beliefs about how these gaps are justified. Furthermore, these beliefs are often consolidated from an early age, reinforced by institutions promoting values such as effort and individual skills to climb socially [@castillo_socialization_2024; @reynolds_perceptions_2014].

At this point we can propose the following research questions: To what extent the preferences for market justice are associated with perceptions of inequality and meritocracy? How stable are these associations (within subjects) along time? The primary objective of this study is to examine the interplay between perceptions of inequality and beliefs in meritocracy, and how their interaction shapes preferences for market justice over time in Chile, using data from the ELSOC panel survey (Chilean Longitudinal Social Study, 2016–2023). The chilean context appears as a particular case for studying market justice preferences given their story of high inequality and strong free-market policies introduced in the dictatorship period and expanded under democratic governments [@madariaga_three_2020; @flores_top_2020]. Additionally, this analysis seeks to explore how political and social contingencies---such as the 2019 and 2022 social movements---might have moderated these relationships by prompting more critical reflection on the commodification of social services [@somma_no_2021]. Recognizing the temporal dimension in shaping market justice preferences is essential, given that historical and contextual factors that could challenge or reaffirm the way in which individuals persceive inequality and meritocracy, and consequantely --- following our argument --- the preferences for market justice.

>>>>

The justification of economic inequality has a long tradition in sociology, with seminal works such as the ones from Kluegel [-@kluegel_social_1995a; -@kluegel_beliefs_1986] and Lane [-@lane_political_1962; -@lane_market_1986]. Lane's main aim was to "help explain the tenacious hold of market capitalism on the public mind" [-@lane_market_1986, p.384], proposing the distinction between market and political justice. Whereas political justice refer to government actions aligned with justice principles such equality or need, market justice involves the allocation linked to earned desserts, particularly through individual contributions based on as effort and ability. Sociological survey research in this area has considered questions related to the extent to which it is considered just to get better access to social services (such as pensions, health and education) based on payment capacity [@busemeyer_skills_2014; @immergut_it_2020; @castillo_socialization_2024; @koos_moral_2019; @lindh_bringing_2023; @lindh_public_2015]. Although these services could be considered basic rights of citizens, evidence to date suggests that a significant portion of the population justifies inequality in these areas [@koos_moral_2019] and that such preferences vary according to objective socioeconomic factors and the contextual characteristics of countries [@lindh_public_2015; @busemeyer_skills_2014]. In the present paper, we argue that there are two other relevant factors to take into account when analyzing differences between individuals and groups to this regard: the perception of economic inequality and the perception of meritocracy.

@@

Along with perception of inequality, a second focus of this paper is the perception of meritocracy. Meritocracy posits that inequality can be legitimized through distributive criteria such as effort and talent [@young_rise_1962; @davis_principles_2001]. Previous studies have demonstrated that people with stronger meritocratic beliefs tend to perceive less inequality as they attribute economic differences to individual achievements [@mijs_paradox_2021; @wilson_role_2003] and also to justify more inequality as these beliefs are associated with attitudes that legitimize status differences [@batruch_belief_2023]. In a context as Chile, where the distribution of goods and services is predominantly governed by market logics strongly introduced during the military dictatorship (1973-1989) [@madariaga_three_2020; @boccardo_30_2020], meritocratic perceptions have the potential to affect the acceptance of social inequalities. Therefore, incorporating the perception of meritocracy in this literature allows for an understanding of how attitudes toward inequality are shaped not only by the perception of economic gaps, but also by beliefs about how these gaps are justified. Furthermore, these beliefs are often consolidated from an early age, reinforced by institutions promoting values such as effort and individual skills to climb socially [@castillo_socialization_2024; @reynolds_perceptions_2014].

At this point we can propose the following research questions: To what extent the preferences for market justice are associated with perceptions of inequality and meritocracy? How stable are these associations (within subjects) along time? The primary objective of this study is to analyze the interplay between perceptions of inequality and meritocracy and their joint influence on preferences for market justice along time in Chile using the panel survey ELSOC (Social Chilean Longitudinal Study, 2016-2023). The chilean case appears as a particular case for studying market justice preferences given their story of high inequality and strong free-market policies introduced in the dictatorship period [@madariaga_three_2020; @flores_top_2020]. Additionally, this analysis seeks to explore how political and social contingencies---such as the 2019 and 2022 social movements---might have moderated these relationships by prompting more critical reflection on the commodification of social services [@somma_no_2021]. Recognizing the temporal dimension in shaping market justice preferences is essential, given that historical and contextual factors that could challenge or reaffirm the way in which individuals persceive inequality and meritocracy, and consequantely --- following our argument --- the preferences for market justice.

### 2025-08-05 resubmission/02-antecedents.qmd
Revert "update resubmit"
This reverts commit 27ec0a816645e6bef02aa45f0b148543bc942541.

Conceptually, *market justice* has been discussed in the literature as a normative principle that legitimates the distribution of economic rewards based on individual merit. It is possible to trace the concept to the understanding of Lane [-@lane_market_1986], who makes a contrast between market justice and political justice. The author defines market justice as a system of "earned deserts", whereby individuals are seen as deserving of a determined distributive outcome due to their effort and skills. In contrast, political justice emphasizes principles of equality and need, which are often represented by the welfare state action through social policies. An important remark is that the principles of market justice rely on the assumption that markets are neutral and self-regulating arenas, where individuals are treated fairly because they face the same formal rules of engagement and procedures [@lane_market_1986]. Consequently, the legitimacy of market justice stems from the assumption that inequalities are not only inevitable but fair---so long as the rules are transparent and opportunities are open. In this way, market justice provides a moral justification for inequality by framing it as a necessary outcome of individual responsibility [@kluegel_legitimation_1999; @lindh_public_2015].

@@

Chile offers an interesting case for examining how public attitudes toward the distribution of social services evolve amid declining poverty and persistently high income inequality within a residual welfare framework [@ferre_welfare_2023]. Following the neoliberal reforms of the 1980s introduced during the civil-military dictatorship (1973-1989), the Chilean welfare state has become increasingly reliant on private provision, with essential services often commodified and largely reserved for those with sufficient purchasing power [@madariaga_three_2020; @boccardo_30_2020]. This model has favored the affluent, while lower-income groups are left dependent on limited and underfunded public alternatives. Research on social stratification characterizes Chile as a society where mobility into intermediate classes is feasible, but access to elite strata remains largely restricted [@lopez-roldan_comparative_2021; @torche_intergenerational_2014a]. While some indicators—such as education and occupation—suggest a relatively fluid class structure, income mobility remains constrained [@espinoza_movilidad_2014].

>>>>

Conceptually, *market justice* has been discussed in the literature as a normative principle that legitimates the distribution of economic rewards based on individual merit. It is possible to trace the concept to the understanding of Lane [-@lane_market_1986], who makes a contrast between market justice and political justice. The author defines market justice as a system of "earned deserts", whereby individuals are seen as deserving of a determined distributive outcome due to their effort and skills. In contrast, political justice emphasizes principles of equality and need, which are often represented by the welfare state action through social policies. An important remark is that the principles of market justice rely on the assumption that markets are neutral and self-regulating arenas, where individuals are treated fairly because they face the same formal rules of engagement [@lane_market_1986]. Consequently, the legitimacy of market justice stems from the assumption that inequalities are not only inevitable but fair---so long as the rules are transparent and opportunities are open. In this way, market justice provides a moral justification for inequality by framing it as a necessary outcome of individual responsibility [@kluegel_legitimation_1999; @lindh_public_2015].

@@

Chile offers an interesting case for examining how public attitudes toward the distribution of social services evolve amid declining poverty and persistently high income inequality within a residual welfare framework [@ferre_welfare_2023]. Following the neoliberal reforms of the 1980s, the Chilean welfare state has become increasingly reliant on private provision, with essential services often commodified and largely reserved for those with sufficient purchasing power [@madariaga_three_2020; @boccardo_30_2020]. This model has favored the affluent, while lower-income groups are left dependent on limited and underfunded public alternatives. Research on social stratification characterizes Chile as a society where mobility into intermediate classes is feasible, but access to elite strata remains largely restricted [@lopez-roldan_comparative_2021; @torche_intergenerational_2014a]. While some indicators—such as education and occupation—suggest a relatively fluid class structure, income mobility remains constrained [@espinoza_movilidad_2014].

### 2025-08-05 resubmission/blinded-paper-resubmit.qmd
Revert "update resubmit"
This reverts commit 27ec0a816645e6bef02aa45f0b148543bc942541.

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "../input/bib/harvard.csl"
# author:
#   - name: Juan Carlos Castillo
#     corresponding: true
#     orcid: 0000-0003-1265-7854
#     email: juancastillov@uchile.cl
#     affiliations:
#       - ref: 1
#       - ref: 2
#       - ref: 3
#   - name: Andreas Laffert
#     orcid: 0000-0002-9008-2454
#     email: alaffertt@estudiante.uc.cl 
#     affiliations:
#       - ref: 4
#   - name: Kevin Carrasco
#     orcid: 0000-0002-9348-8361
#     email: kevin.carrasco@ug.uchile.cl
#     affiliations:
#       - ref: 2
#   - name: Julio Iturra-Sanhueza
#     orcid: 0000-0003-1993-3479
#     email: julioiturrasanhueza@gmail.com 
#     affiliations:
#       - ref: 5     
# affiliations: 
#   - id: 1
#     name: Departamento de Sociología, Universidad de Chile
#   - id: 2
#     name: Centro de estudios del conflicto y cohesión social (COES)
#   - id: 3
#     name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
#   - id: 4
#     name: Instituto de Sociología, Pontificia Universidad Católica de Chile
#   - id: 5
#     name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
 Several countries have experienced a shift toward the privatization and commodification of public goods, welfare policies, and social services. In Latin America, Chile stands out as a paradigmatic case where this trend has led to the extensive marketization of essential services. From a moral economy perspective, the extent to which individuals consider it fair for access to such services to depend on market criteria has been conceptualized as market justice preferences. This study investigates the relationship between perceptions of economic inequality, meritocratic beliefs, and market justice preferences in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey – ELSOC ($N_{observations}$ = 8,643; $N_{individuals}$ = 1,687), the analysis examines how subjective assessments of inequality shape attitudes toward the role of merit in access to key social services such as healthcare, education, and pensions. The findings show that greater perceived inequality is associated with lower market justice preferences. However, individuals who believe that effort is rewarded are more likely to legitimize existing disparities. In contrast, the perception that talent is rewarded shows a negative effect on market justice preferences; an effect that intensifies as perceived inequality increases over time. The study also considers the influence of major social movements during this period, which appear to have reshaped public discourse on justice and fairness. These findings contribute to a deeper understanding of how distributive beliefs evolve in contexts marked by persistent inequality and entrenched neoliberal frameworks.
  \newline
  **Keywords**: Inequality perception, meritocracy, commodification, Chile, public preferences 
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

>>>>

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "input/bib/harvard.csl"
# author:
#   - name: Juan Carlos Castillo
#     corresponding: true
#     orcid: 0000-0003-1265-7854
#     email: juancastillov@uchile.cl
#     affiliations:
#       - ref: 1
#       - ref: 2
#       - ref: 3
#   - name: Andreas Laffert
#     orcid: 0000-0002-9008-2454
#     email: alaffertt@estudiante.uc.cl 
#     affiliations:
#       - ref: 4
#   - name: Kevin Carrasco
#     orcid: 0000-0002-9348-8361
#     email: kevin.carrasco@ug.uchile.cl
#     affiliations:
#       - ref: 2
#   - name: Julio Iturra-Sanhueza
#     orcid: 0000-0003-1993-3479
#     email: julioiturrasanhueza@gmail.com 
#     affiliations:
#       - ref: 5     
# affiliations: 
#   - id: 1
#     name: Departamento de Sociología, Universidad de Chile
#   - id: 2
#     name: Centro de estudios del conflicto y cohesión social (COES)
#   - id: 3
#     name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
#   - id: 4
#     name: Instituto de Sociología, Pontificia Universidad Católica de Chile
#   - id: 5
#     name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
 Several countries have experienced a shift toward the privatization and commodification of public goods, welfare policies, and social services. In Latin America, Chile stands out as a paradigmatic case where this trend has led to the extensive marketization of essential services. From a moral economy perspective, the extent to which individuals consider it fair for access to such services to depend on market criteria has been conceptualized as market justice preferences. This study investigates the relationship between perceptions of economic inequality, meritocratic beliefs, and market justice preferences in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey – ELSOC ($N_{observations}$ = 8,643; $N_{individuals}$ = 1,687), the analysis examines how subjective assessments of inequality shape attitudes toward the role of merit in access to key social services such as healthcare, education, and pensions. The findings show that greater perceived inequality is associated with lower market justice preferences. However, individuals who believe that effort is rewarded are more likely to legitimize existing disparities. In contrast, the perception that talent is rewarded shows a negative effect on market justice preferences; an effect that intensifies as perceived inequality increases over time. The study also considers the influence of major social movements during this period, which appear to have reshaped public discourse on justice and fairness. These findings contribute to a deeper understanding of how distributive beliefs evolve in contexts marked by persistent inequality and entrenched neoliberal frameworks
  \newline
  **Keywords**: Economic inequality, meritocracy, market justice, Chile, public preferences, inequality perception
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

### 2025-08-05 resubmission/paper-resubmit.qmd
Revert "update resubmit"
This reverts commit 27ec0a816645e6bef02aa45f0b148543bc942541.

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "../input/bib/harvard.csl"
author:
  - name: Juan Carlos Castillo
    corresponding: true
    orcid: 0000-0003-1265-7854
    email: juancastillov@uchile.cl
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
  - name: Andreas Laffert
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 4
  - name: Kevin Carrasco
    orcid: 0000-0002-9348-8361
    email: kevin.carrasco@ug.uchile.cl
    affiliations:
      - ref: 2
  - name: Julio Iturra-Sanhueza
    orcid: 0000-0003-1993-3479
    email: julioiturrasanhueza@gmail.com 
    affiliations:
      - ref: 5     
affiliations: 
  - id: 1
    name: Departamento de Sociología, Universidad de Chile
  - id: 2
    name: Centro de estudios del conflicto y cohesión social (COES)
  - id: 3
    name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
  - id: 4
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
  - id: 5
    name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
 Several countries have experienced a shift toward the privatization and commodification of public goods, welfare policies, and social services. In Latin America, Chile stands out as a paradigmatic case where this trend has led to the extensive marketization of essential services. From a moral economy perspective, the extent to which individuals consider it fair for access to such services to depend on market criteria has been conceptualized as market justice preferences. This study investigates the relationship between perceptions of economic inequality, meritocratic beliefs, and market justice preferences in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey – ELSOC ($N_{observations}$ = 8,643; $N_{individuals}$ = 1,687), the analysis examines how subjective assessments of inequality shape attitudes toward the role of merit in access to key social services such as healthcare, education, and pensions. The findings show that greater perceived inequality is associated with lower market justice preferences. However, individuals who believe that effort is rewarded are more likely to legitimize existing disparities. In contrast, the perception that talent is rewarded shows a negative effect on market justice preferences; an effect that intensifies as perceived inequality increases over time. The study also considers the influence of major social movements during this period, which appear to have reshaped public discourse on justice and fairness. These findings contribute to a deeper understanding of how distributive beliefs evolve in contexts marked by persistent inequality and entrenched neoliberal frameworks
  \newline
 **Keywords**: Inequality perception, meritocracy, commodification, Chile, public preferences 
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

>>>>

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  docx:
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/merit-edjust.bib"
# csl: "input/bib/apa6.csl"
csl: "../input/bib/harvard.csl"
author:
  - name: Juan Carlos Castillo
    corresponding: true
    orcid: 0000-0003-1265-7854
    email: juancastillov@uchile.cl
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
  - name: Andreas Laffert
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 4
  - name: Kevin Carrasco
    orcid: 0000-0002-9348-8361
    email: kevin.carrasco@ug.uchile.cl
    affiliations:
      - ref: 2
  - name: Julio Iturra-Sanhueza
    orcid: 0000-0003-1993-3479
    email: julioiturrasanhueza@gmail.com 
    affiliations:
      - ref: 5     
affiliations: 
  - id: 1
    name: Departamento de Sociología, Universidad de Chile
  - id: 2
    name: Centro de estudios del conflicto y cohesión social (COES)
  - id: 3
    name: Núcleo milenio de desigualdades y oportunidades digitales (NUDOS)
  - id: 4
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
  - id: 5
    name: International Graduate School of Social Sciencies (BIGSSS), University of Bremen, Germany
citeproc: true
abstract: | 
 Several countries have experienced a shift toward the privatization and commodification of public goods, welfare policies, and social services. In Latin America, Chile stands out as a paradigmatic case where this trend has led to the extensive marketization of essential services. From a moral economy perspective, the extent to which individuals consider it fair for access to such services to depend on market criteria has been conceptualized as market justice preferences. This study investigates the relationship between perceptions of economic inequality, meritocratic beliefs, and market justice preferences in Chile between 2016 and 2023. Using six waves of panel data from the Chilean Longitudinal Social Survey – ELSOC ($N_{observations}$ = 8,643; $N_{individuals}$ = 1,687), the analysis examines how subjective assessments of inequality shape attitudes toward the role of merit in access to key social services such as healthcare, education, and pensions. The findings show that greater perceived inequality is associated with lower market justice preferences. However, individuals who believe that effort is rewarded are more likely to legitimize existing disparities. In contrast, the perception that talent is rewarded shows a negative effect on market justice preferences; an effect that intensifies as perceived inequality increases over time. The study also considers the influence of major social movements during this period, which appear to have reshaped public discourse on justice and fairness. These findings contribute to a deeper understanding of how distributive beliefs evolve in contexts marked by persistent inequality and entrenched neoliberal frameworks
  \newline
  **Keywords**: Economic inequality, meritocracy, market justice, Chile, public preferences, inequality perception
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---
